\chapter{Background}
\label{chap:background}
This section introduces and explain key points and concepts which are essential to understanding the context and application of this study.

\section{User Experience}
User experience (UX) design is a conceptual design practice, which has its roots in human-computer interaction, functional design and ergonomics. The term \textit{user experience design} was first coined by Norman, a user experience architect, who thought that the terms human interface and usability were too narrow \cite{Merholz2007}. Norman wanted to cover all different aspects of the user's experience with a product; "including industrial design graphics, the interface, the physical interaction and the manual". Since the field's conception, and as it has been used in scientific literature and professionally, there is been exhaustive literary and scientific efforts to define the field and its concerns \cite{Law2008} \cite{Law2009} \cite{Forlizzi2000}. Hassenzahl \cite{Hassenzahl2006}, a German psychologist, has defined it as;
\begin{displayquote}
  User experience is about technology that fulfills more than just instrumental needs in a way that acknowledges its use as a subjective, situated, complex and dynamic encounter. UX is a consequence of a user's internal state (predispositions, expectations, needs, motivation, mood, etc.), the characteristics of the designed system (e.g. complexity, purpose, usability, functionality, etc.) and the context (or the environment) within which the interaction occurs (e.g. organizational/social setting, meaningfulness of the activity, voluntariness of use, etc.)
\end{displayquote}

\subsection{Mobile UX}
The use of mobile phones is becoming increasingly pervasive; people carry their smart devices almost anywhere \cite{Mallat2004}. With the usage pattern of discontinued use, "micro-breaks" \cite{McGregor2014a}, the small form factor and the wide range of different possible contexts of use \cite{Wang2016}, designing interaction for mobile devices requires its own research methods, tools and infrastructure to overcome these challenges \cite{Nakhimovsky2009}. The possibilities of mobile devices enable us to communicate more with our family and friends, stay more informed, innovative, productive etc \cite{Wang2016}.

The most commonly used phone model today are smart phones. Smart phones usually have features such as full-color screen, camera \cite{Yu2012}, voice and data communication, multimedia consumption, mobile gaming, and GPS navigation \cite{Ruiz2011}. The devices form factor limit the possible input and outputs. The two primary means of input supported by this kind of devices are
\begin{enumerate*}[label=(\(\arabic*\))]
  \item Touchscreen and
  \item Sensors
\end{enumerate*}

The sensors available are dependent on the device, but accelerometers, gyroscopes and orientation sensors are the most common. The touchscreen enables the user to interact through two-dimensional surface gestures \cite{Ruiz2011}. It is also possible for the user to gesture in three dimensions using the sensors, but we will focus mostly on two-dimensional gestures. The possible actions and models which we interact through with mobile devices are mostly based on hand-based gestures. The gesture model which we have for touchscreen-based mobile devices include tapping, swiping and shaking.

\section{Onboarding}
The term onboarding is a quite recent term \cite{Dai2007}. Onboarding stems from a business, management and human-resource context, and it describes a process to introduce and help a new employee become an effective member of their new organization by teaching them the knowledge, skills and behaviors required to succeed \cite{Bauer2011}. Graybill et al. state that onboarding is an important aspect to reduce the time for the employee to be a fully functional and engaged member of the new company \cite{GraybillJolieO;HudsonCarpenterMariaTaesil;OffordJeromeJr;PiorunMary;Shaffer2013}. Bradt et al. define onboarding as "the process of acquiring, accommodating, assimilating, and accelerating new team members, whether they come from outside or inside the organization" \cite{Bradt2009}. Crumlish et al. \cite{Crumlish2009} write that this definition and process apply well with user onboarding.

\subsection{User onboarding}
While there is some literature about user onboarding \cite{Thomsen2016}, the most notable contributions to the research field of user onboarding is by Oechsner \cite{Oechsner2016}, where she presents general guidelines for onboarding a user to a digital platform. The guidelines she presents are supported by psychology and IxD research but fail to include the body of work of employee onboarding and the marketing aspect \textit{stickiness}. Also, her guidelines are meant to be general and may not alone aid the entire onboarding process of all platforms. Her study of user onboarding has been exhaustive, but with the circumstances related to the different usage model of mobile applications, the need for revisiting the research of user onboarding is supported.
